\documentclass[12pt]{article}
\usepackage{ctex}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{nameref}
\usepackage{fancyhdr}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,float}
\usepackage{physics}
\usepackage{pgfplots}
\usepackage[a4paper, total={6in, 9in}]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyhf[FL]{Mok-DSE-MATH-CP}
\fancyhf[CF]{\thepage}

\newcommand{\innerprod}[2]{\langle{#1},{#2}\rangle}
\newcommand{\id}{\mathtt{id}}

\newtheorem*{definition}{Definition}
\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}
\newtheorem*{lemma}{Lemma}
\newtheorem*{proposition}{Proposition}
\newtheorem*{remark}{Remark}
\newtheorem*{claim}{Claim}
\newtheorem*{example}{Example}
\newtheorem*{axiom}{Axiom}

\begin{document}
    \thispagestyle{plain}

    \centering 

    \section*{HKDSE MOCK EXAM PAPER\\MATHEMATICS Compulsory Part\\Question-Answer Book\\Set 1}

    Time allowed: 2 hours 15 minutes

    Name:\hrulefill \hfill Marks:\hrulefill/105

    \raggedright

    \subsection*{Instructions}

    \begin{enumerate}
        \item This paper must be answered in English.
        \item Unless otherwise specified, all working must be clearly shown.
        \item Unless otherwise specified, numerical answers must be exact.
        \item This paper is for \textbf{internal use} only.
        \item All questions are constructed by Mok Owen.
        \item The mock paper is composed of 3 parts, including Section A(1), Section A(2) and Section B. Each part consist of 35 marks each.
    \end{enumerate}

    \newpage

    \subsection*{Section A(1) (35 marks)}

    \begin{enumerate}
        \item Simplify $\dfrac{(mn^{-2})^3}{m^{-1}}$ and express your answer with positive indices.\hfill (3 marks)
        \item Make $a$ the subject of the formula $\dfrac{a+1}{a-1}=\dfrac{b+c}{d-c}$.\hfill (3 marks)
        \item Factorize \begin{enumerate}
            \item $4x^2+4xy+y^2$,
            \item $12x^2+xz+z^2$,
            \item $(4x^2+4xy+y^2)-(12x^2+xz+z^2)$.
        \end{enumerate}\hfill (3 marks)
        \item Given that $a:b=5:6$ and $2b=3c$.\begin{enumerate}
            \item Find $a:b:c$.
            \item Find the value of $\dfrac{9a+2b+3c}{a+b+c}$.
        \end{enumerate}\hfill (3 marks)
        \item Given a stock X in the market at \$x per unit at instance. It is known that a person could buy a certain amount of stock X at this price level. What is the percentage change in amount affordable for that person if the stock price is increased by 20\% ?\hfill (4 marks)
        \item Consider the compound inequality \begin{align*}
            \begin{cases}
                \dfrac{x}{x+1}\leq 5\\
                3x+2\leq 0
            \end{cases}
        \end{align*}
        \begin{enumerate}
            \item Solve the inequality system.
            \item Write down the number of integers satisfying the inequality.
        \end{enumerate}\hfill (4 marks)
        \item Let $f(x)=x^2-kx-(k+1)$ has equal roots. Find \begin{enumerate}
            \item $k$,
            \item the possible y-intercepts of $y=kf(x)$.
        \end{enumerate}\hfill (5 marks)
        \item 
    \end{enumerate}

\end{document}